Lyman-$\alpha$ line emission sketches of a massive dwarf galaxy

### 2017-02-07 paper/letter.tex
theory

\section{Theoretical Models}

@@

The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In this paper we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line.

The first important effect of rotation is that it breaks the spherical
symmetry of the static case. 
Now the line's observed morphology depends on the angle $\theta$ between the
line-of-sight (LOS) and the rotation axis. 
LOS parallel to the rotation axis tend to observed the line without
any modification from rotation, while the perpendicular LOS will
observe a maximal change in the line's morphology due to rotation.

The main change in the line's morphology is that it broadens and the
intensity at the center increases. 
For high enough rotational velocities the intensity at the peak's
center increases so much that the line goes from double to single
peaked, sometimes slightly triple peaked.
This is the feature that allows this model to fit the observational
features of \tol.

\citep{GaravitoCamargo2014} derived a concise analytical description for
those features. 
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya\ photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
Using the analytical solution for the \lya\ spectra of a static sphere
plus the right frequency shifts  computed from geometrical
considerations, one is able to compute an analytical solution for the
rotating sphere that reproduces the main features found using the full
numerical simulation.

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations for
a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers ecplore
the parameter space sampling the likelihood function.

>>>>

\section{Theoretical Models and Parameter Exploration}

@@

The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.  {\bf These parameters are: MAX}

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report do not include any dust model.
In this paper we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line as explained by \citet{GaravitoCamargo2014}.

The analytical solution for the rotation sphere is the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers ecplore
the parameter space sampling the likelihood function.
